### 2022-03-02 paper2.tex
Updates

The lack of research in which vehicles are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and wellbeing of
individuals in our society. Even outside of the misinformation literature, much
of the research conducted in social networks and communication focus on senders,
influencers, and persuasion strategies 
\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955, lazarsfeldPeopleChoice1944},
rather than on
“the receiver as an active information seeker and processor." \citep{johnsonComprehensiveModelCancerRelated1993},
though there are always exceptions \cite{ysenbach09}

@@

Active, directed searching by individuals to obtain information is sparsely
discussed in the sociological literature. Pejtersen \citet{pejtersen1984}, a scholar
of library and information science, theorized that there are 5 strategies for
searching for information. The most common strategy is browsing, where people
follow leads based on associations without premeditation. Another strategy is
analytical, which includes an explicit consideration of all facets of the
question to guide a search. The empirical method guides the search based on
tactics that were successful in past research. The known site strategy is to go
to the direct source of the information if known. And finally, the similarity
method is to find information based on another similar question that already has
an answer. These 5 strategies vary in their demands for prior knowledge,
cognitive processing, memory, and time spent. While this theory is aimed at
finding information in a library setting, scholars have extended the theory to
other fields and validated the framework
\citep{fidelHumanInformationInteraction2012}; the frame is a useful beginning point
for my theories of information search through network activation or through
computer-mediated communication.

@@

%%% STOPED PASTING CITATIONS HERE

@@

There are important factors that can influence information-seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}
. UGT
posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s  \citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible with
Lazarsfeld and Katz’s theory of two-step flow \cite{katzPersonalInfluencePart1955}
because people can choose their media and the opinion leaders they follow.
Modern-day theorists have extended UGT theory and classified the uses and
gratifications of the internet and of social media. \cite{staffordDeterminingUsesGratifications2004} theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties. \cite{leungGenerationalDifferencesContent201} theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

Adapting these facets of UGT and social support to my own case, I theorize that
online search allows for increased anonymity, a lowered social cost, and the
potential avoidance of embarrassment and other negative social interactions,
especially in the case on search engines. Stephen Rains
(2018) finds that patients tend to search for
technical information about an illness online but they then turn to their social
network for experiential information from others facing similar circumstances in
the case of cancer. The type of information sought is therefore important.
If specific expertise on a specific topic is desired by a searcher, they may
reach out to personal connections that they see as expert such as a doctor, or
if an individual distrusts the medical establishment, they may be more likely to
activate informational support among their social network or turn to online
groups that validate their worldview (Bogers and Wernersen 2014). Finally, UGT and
Brasher's definition of social support
(2002) help us to theorize that the
psychosocial needs like identity management or relational maintenance
(Brashers et al. 2002) of an individual may influence their
chosen information search vehicle: when the informational need is related to
forming and deepening social ties search is likely to be done from network ties.

@@

The data used for this research project are based on original survey data
sampled between December 03, 2021 through
December 12, 2021. This survey was hosted on Qualtrics and
participants were paid and recruited using Amazon Turk (MTurk). The total valid
survey responses (\emph{n} = 948) were selected from a total of 1,066
respondents; some responses were disqualified due to a few factors such as
detected usage of a VPN, random answer clicking (determined by illogical
responses), poor quality typed responses (e.g., social network alters
consistently named random nouns), or taking the survey more than once. The same
is slighted gender unbalanced, slightly skewing towards a male sample. For the
respondents who provided their zip code (p =
0.98), the
sample is quite balanced with a slight skew towards MTurkers in the South (p =
0.41).
The survey took an average of 24.48 minutes with a
standard deviation of 13.23 minutes. The shortest
valid survey took 3.75 minutes and the longest took
111.08 minutes. Participants were paid \$6.00 for their
time after Amazon administrative fees, funded by a Grant awarded to Kelsey E.
Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social
Science and the Russell Sage Foundation. The main portion of this survey
replicates the book, Someone to Talk To (Small 2017) by expanding on
Small's finding that people draw on much broader sources than ``important people''
for support by segregating weak-tie social support into instrumental, emotional,
and informational support (see House et al. 1988). The latter
part of the survey focuses on resource activation for the specific case-study of
information during the Covid-19 pandemic analyzed in this paper.

\begin{table}[!h]

\caption{\label{tab:table-1-desc}Descriptive Statistics for Dichotomous and Numeric Variables}
\centering
\begin{tabular}[t]{lrr}
\toprule
  & Mean & SD\\
\midrule
\cellcolor{gray!6}{Received info} & \cellcolor{gray!6}{\num{0.66}} & \cellcolor{gray!6}{\num{0.47}}\\
Received info, Doctor & \num{0.47} & \num{0.50}\\
\cellcolor{gray!6}{Received info, Person} & \cellcolor{gray!6}{\num{0.67}} & \cellcolor{gray!6}{\num{0.47}}\\
Received info, News & \num{0.65} & \num{0.48}\\
\cellcolor{gray!6}{Received info, Social Networking Site} & \cellcolor{gray!6}{\num{0.40}} & \cellcolor{gray!6}{\num{0.49}}\\
Received info, Online Forum & \num{0.35} & \num{0.48}\\
\cellcolor{gray!6}{Sought Info} & \cellcolor{gray!6}{\num{0.78}} & \cellcolor{gray!6}{\num{0.41}}\\
Sought Info, Doctor & \num{0.44} & \num{0.50}\\
\cellcolor{gray!6}{Sought Info, Person} & \cellcolor{gray!6}{\num{0.42}} & \cellcolor{gray!6}{\num{0.49}}\\
Sought Info, Social Networking Site & \num{0.18} & \num{0.39}\\
\cellcolor{gray!6}{Sought Info, Online Forum} & \cellcolor{gray!6}{\num{0.27}} & \cellcolor{gray!6}{\num{0.44}}\\
Sought Info, Online Search & \num{0.41} & \num{0.49}\\
\cellcolor{gray!6}{Vaccination Status} & \cellcolor{gray!6}{\num{0.84}} & \cellcolor{gray!6}{\num{0.36}}\\
Vaccination Outlook & \num{0.87} & \num{0.34}\\
\cellcolor{gray!6}{Age} & \cellcolor{gray!6}{\num{37.76}} & \cellcolor{gray!6}{\num{10.75}}\\
Hispanic or Latino/x & \num{0.15} & \num{0.36}\\
\cellcolor{gray!6}{Race, White} & \cellcolor{gray!6}{\num{0.88}} & \cellcolor{gray!6}{\num{0.33}}\\
Race, Black & \num{0.08} & \num{0.27}\\
\cellcolor{gray!6}{Race, Native American} & \cellcolor{gray!6}{\num{0.03}} & \cellcolor{gray!6}{\num{0.16}}\\
Race, Asian or Pacific Islander & \num{0.04} & \num{0.20}\\
\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.74}} & \cellcolor{gray!6}{\num{0.44}}\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
\end{tabular}
\end{table}

@@

Further dependent variables segment the above question into multiple options;
``How did you look for information about the Covid-19 vaccine?'' Respondents were
posed with 5 responses and `other,' of which they could select multiple. The
largest proportion, 44\%, asked their
`doctor or another health professional' (95\% Confidence Interval =
\{41\%, 47\%\}).
About 42\% said they asked, `a person
like friend, neighbor, or family member that {[}they{]} know' (95\% Confidence
Interval = \{39\%, 45\%\}). An additional
41\% searched `for {[}their{]} question
using an online search engine such as Google or Bing' (95\% Confidence Interval
= \{38\%, 45\%\}). About a quarter of the
sample, 27\%, `posted queries in an
online discussion group, listserve, or other online forum like a Facebook Group
or Subreddit' (95\% Confidence Interval = \{24\%, 30\%\}).
And finally, 18\% of the sample `posted queries
on a social networking site such as Facebook timeline, Twitter status update, or
LinkedIn' (95\% Confidence Interval = \{16\%, 21\%\}).
Much of the question wording and the specific categories of search were inspired
by ICPSR project 37220 (Scanlon 2019).

\begin{table}[!h]

\caption{\label{tab:table-2-desc}Descriptive Statistics for Categorical Variables}
\centering
\begin{tabular}[t]{llrr}
\toprule
  &    & N & Percent\\
\midrule
\cellcolor{gray!6}{Gender} & \cellcolor{gray!6}{Female} & \cellcolor{gray!6}{418} & \cellcolor{gray!6}{\num{44.09}}\\
 & Male & 524 & \num{55.27}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Other} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{\num{0.63}}\\
Highest Education Level & Graduate or professional degree & 145 & \num{15.30}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Bachelor's degree} & \cellcolor{gray!6}{560} & \cellcolor{gray!6}{\num{59.07}}\\
 & Associate's or Technical degree & 72 & \num{7.59}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Some college} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{\num{10.55}}\\
 & High school graduate & 68 & \num{7.17}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Less than high school} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{\num{0.32}}\\
Plan to be Vaccinated if not & Probably not & 38 & \num{4.01}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Definitely yes} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{\num{1.37}}\\
 & Definitely not & 61 & \num{6.43}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Might or might not} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{\num{2.32}}\\
 & Probably yes & 13 & \num{1.37}\\
\cellcolor{gray!6}{Found Info Sought Useful} & \cellcolor{gray!6}{Very useful} & \cellcolor{gray!6}{345} & \cellcolor{gray!6}{\num{36.39}}\\
 & Moderately useful & 112 & \num{11.81}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Extremely useful} & \cellcolor{gray!6}{264} & \cellcolor{gray!6}{\num{27.85}}\\
 & Slightly useful & 18 & \num{1.90}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Not at all useful} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{\num{0.21}}\\
Census Region & Midwest & 171 & \num{18.04}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Northeast} & \cellcolor{gray!6}{170} & \cellcolor{gray!6}{\num{17.93}}\\
 & South & 365 & \num{38.50}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{West} & \cellcolor{gray!6}{223} & \cellcolor{gray!6}{\num{23.52}}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
\end{tabular}
\end{table}

@@

Another Dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received or plans to receive a vaccination against Covid-19. For this survey, the number of doses or timeline of receipt were less
relevant to the research question. This variable instead focuses on intent or
opinion about the vaccine. About 87\% have a
positive view about the vaccine. This construct is made through the combination
of two survey items. The first item is actual vaccination status, obtained through
the question `Did you receive a Covid-19 vaccine?'
84\% of the sample said that
they had indeed received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}). As the national vaccination rate is
closer to 75\% (CDC 2020a), this indicates some bias in our sample that must be
acknowledged: either MTurkers are more likely to be vaccinated that the normal
population (sampling bias) or there is some conformity bias in the responses
causing survey takers to provide false answers. The second survey item that
contributes to `Vaccination Outlook' was only given to those who had not
responded `yes' to the to their vaccination status. These respondents were asked `Do you
plan to receive a vaccine for the prevention of the Covid-19 virus?' Of those
who were asked this question (n = 147),
9\%
said they were `definitely yes' getting the vaccine;
9\%
said they were `probably yes' going to receive vaccine. The rest of the sample was more unsure:
15\%
said they `Might or might not,'
26\%
said `Probably not,' and finally
41\%
said they would `definitely not' receive the vaccine. The variable `Vaccination
Outlook' indicates that either the respondent received a Covid-19 vaccine or
either probably or definitely will in the future.

@@

My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-desc}
\& \ref{tab:table-2-desc}, I present descriptive statistics for all study
variables, including variable ranges, means, and standard deviations. For this
paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
fit a series of Binomial Generalized Linear Models (Venables and Ripley 2002). In Table \ref{tab:table-model-1}\footnote{All tables in this paper were created with the modelsummary package in \texttt{r} (Arel-Bundock 2022)}
, I fit a logistic regression model predicting
whether someone sought information about Covid-19 using their sources of
information (`Received info') as well as various demographic variables such as
age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
the relationship between the coefficients and information seeking.\footnote{Figures in
  this paper were all created using the \texttt{r} packages jtools (Long 2020) and ggplot2 (Wickham 2011; Wickham, Chang, and Henry n.d.)}.
In Table \ref{tab:model-2-phi} I disaggregate information seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about Covid-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient (Warrens 2008), otherwise
known as a mean square contingency coefficient which is used to investigate the
degree of association between two binary variables.\footnote{To calculate the Phi
  Coefficient, I utilize the Psych \texttt{r} package (Revelle 2015)} I then investigate the
associations between my predictors and the 5 information search vehicles by
modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook. Figure \ref{fig:plot-model-3} then
illustrates the relationship between the coefficients and vaccination outlook.

@@

\begin{table}[!h]

\caption{\label{tab:table-model-1}What predicts someone intentionally searched for information}
\centering
\begin{tabular}[t]{lc}
\toprule
  & Model 1\\
\midrule
\cellcolor{gray!6}{Received Info, Doctor} & \cellcolor{gray!6}{\num{1.037}*** (\num{0.181})}\\
Received Info, Person & \num{0.624}*** (\num{0.171})\\
\cellcolor{gray!6}{Received Info, News} & \cellcolor{gray!6}{\num{0.316}+ (\num{0.175})}\\
Received Info, Social Networking Site & \num{0.320}+ (\num{0.187})\\
\cellcolor{gray!6}{Received Info, Online Forum} & \cellcolor{gray!6}{\num{0.873}*** (\num{0.203})}\\
Age & \num{0.025}** (\num{0.009})\\
\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.456}* (\num{0.192})}\\
White & \num{0.857} (\num{0.575})\\
\cellcolor{gray!6}{Black} & \cellcolor{gray!6}{\num{1.274}* (\num{0.625})}\\
Native American & \num{0.405} (\num{0.710})\\
\cellcolor{gray!6}{Asian} & \cellcolor{gray!6}{\num{0.105} (\num{0.588})}\\
Hispanic or Latino/x & \num{0.425} (\num{0.271})\\
\cellcolor{gray!6}{Num.Obs.} & \cellcolor{gray!6}{\num{948}}\\
\midrule
$R_{McFadden}^2$ & \num{0.110}\\
\cellcolor{gray!6}{BIC} & \cellcolor{gray!6}{\num{988.1}}\\
Log.Lik. & \num{-442.618}\\
\bottomrule
\multicolumn{2}{l}{\rule{0pt}{1em}Raw, Unexponentiated Coefficients}\\
\multicolumn{2}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}
\end{table}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-model-1-1}

}

\caption{Plot of Coefficients, Model 1}\label{fig:plot-model-1}
\end{figure}

@@

\begin{table}[!h]

\caption{\label{tab:model-2-phi}Phi Coefficient ($\phi$) of binary association between each Information Search Vehicle}
\centering
\begin{tabular}[t]{l|l|r|r|r|r}
\hline
 & Person & Dr & Online Forum & Social Networking Site & Online Search\\
\hline
\cellcolor{gray!6}{Person} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.28} & \cellcolor{gray!6}{0.172} & \cellcolor{gray!6}{0.275} & \cellcolor{gray!6}{0.216}\\
\hline
Dr & NA & NA & 0.192 & 0.152 & 0.098\\
\hline
\cellcolor{gray!6}{Online Forum} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.371} & \cellcolor{gray!6}{-0.073}\\
\hline
Social Networking Site & NA & NA & NA & NA & 0.057\\
\hline
\cellcolor{gray!6}{Online Search} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA}\\
\hline
\end{tabular}
\end{table}

To further investigate how people search for information, I asked those who had
sought information out intentionally, ``How did you look for information about
the Covid-19 vaccine?'' Because respondents could select as many responses as
applicable, each response is recorded as a dichotomous variable. Table
\ref{tab:table-1-desc} reveals differences in the prevalence of usage of the
various information seeking vehicles: Around 40\% of the sample has inquired for
information from a doctor, a person, or using online search tool (
44\%,
42\%,
41\%) while my
respondents used vehicles like online forums (
27\%) and social
networking sites (18\%)
to seek out information at significantly lower rates. To investigate how each
Information Search Vehicle are related to each other using the Phi Coefficient
(\(\\phi\)) of binary association between each Information Search Vehicle pair.
The Phi coefficient can be interpreted like a correlation coefficient, with
numbers closer to -1 or positive one indicating a very strong relationship
(Warrens 2008). Table \ref{tab:model-2-phi} shows the results of these
coefficients. Out of the five information search vehicles investigated, there is
evidence that the vehicles are distinctly different concepts because most
coefficients fall under 0.3, the general rule of thumb for correlation
coefficients to indicate a relationship. There does seem to be a relationship
between Online Forums and Social Networking Sites, possibly due to an
individual's propensity to use online networks over in-person networks. These
coefficients indicate a weak relationship between any two vehicles of
information search and that respondents in my sample utilize each of these a
little bit differently.

\begin{table}[!h]

\caption{\label{tab:table-model-2}What predicts someone intentionally searched for information, by vehicle of information search}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Dependent Variable} \\
\cmidrule(l{3pt}r{3pt}){2-6}
  & Doctor & Person & Online Forum & Social Networking Site & Online Search\\
\midrule
\cellcolor{gray!6}{Received Info, Doctor} & \cellcolor{gray!6}{\num{1.942}***} & \cellcolor{gray!6}{\num{1.124}***} & \cellcolor{gray!6}{\num{0.181}} & \cellcolor{gray!6}{\num{0.540}**} & \cellcolor{gray!6}{\num{0.430}**}\\
Received Info, Person & \num{0.800}*** & \num{1.199}*** & \num{0.728}*** & \num{0.281} & \num{0.365}*\\
\cellcolor{gray!6}{Received Info, News} & \cellcolor{gray!6}{\num{0.437}**} & \cellcolor{gray!6}{\num{0.100}} & \cellcolor{gray!6}{\num{0.359}*} & \cellcolor{gray!6}{\num{0.514}*} & \cellcolor{gray!6}{\num{1.091}***}\\
Received Info, Social Networking Site & \num{-0.130} & \num{0.437}** & \num{-0.603}** & \num{0.731}*** & \num{1.272}***\\
\cellcolor{gray!6}{Received Info, Online Forum} & \cellcolor{gray!6}{\num{0.412}*} & \cellcolor{gray!6}{\num{0.263}+} & \cellcolor{gray!6}{\num{1.266}***} & \cellcolor{gray!6}{\num{0.974}***} & \cellcolor{gray!6}{\num{0.695}***}\\
Age & \num{0.002} & \num{0.001} & \num{-0.007} & \num{-0.003} & \num{0.029}***\\
\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.542}**} & \cellcolor{gray!6}{\num{0.154}} & \cellcolor{gray!6}{\num{1.086}***} & \cellcolor{gray!6}{\num{1.344}***} & \cellcolor{gray!6}{\num{-0.952}***}\\
White & \num{0.631} & \num{0.245} & \num{0.009} & \num{0.559} & \num{0.012}\\
\cellcolor{gray!6}{Black} & \cellcolor{gray!6}{\num{0.366}} & \cellcolor{gray!6}{\num{0.208}} & \cellcolor{gray!6}{\num{0.608}} & \cellcolor{gray!6}{\num{0.646}} & \cellcolor{gray!6}{\num{0.357}}\\
Native American & \num{0.309} & \num{-0.696} & \num{0.209} & \num{0.762} & \num{-0.831}\\
\cellcolor{gray!6}{Asian} & \cellcolor{gray!6}{\num{-0.294}} & \cellcolor{gray!6}{\num{-0.566}} & \cellcolor{gray!6}{\num{-2.496}**} & \cellcolor{gray!6}{\num{-0.568}} & \cellcolor{gray!6}{\num{0.634}}\\
Hispanic or Latino/x & \num{0.324} & \num{0.116} & \num{0.529}* & \num{0.632}** & \num{-0.585}*\\
\cellcolor{gray!6}{Num.Obs.} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}}\\
\midrule
$R_{McFadden}^2$ & \num{0.193} & \num{0.121} & \num{0.145} & \num{0.154} & \num{0.221}\\
\cellcolor{gray!6}{BIC} & \cellcolor{gray!6}{\num{1152.2}} & \cellcolor{gray!6}{\num{1237.6}} & \cellcolor{gray!6}{\num{1048.0}} & \cellcolor{gray!6}{\num{864.8}} & \cellcolor{gray!6}{\num{1104.6}}\\
Log.Lik. & \num{-524.709} & \num{-567.376} & \num{-472.576} & \num{-380.971} & \num{-500.907}\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}Raw, Unexponentiated Coefficients}\\
\multicolumn{6}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}}
\end{table}

@@

\begin{table}[!h]

>>>>

The lack of research in which vehicles are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and wellbeing of
individuals in our society. Even outside of the misinformation literature, much
of the research conducted in social networks and communication focus on senders,
influencers, and persuasion strategies 
\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955, lazarsfeldPeopleChoice1944},
rather than on
“the receiver as an active information seeker and processor." \citep{johnsonComprehensiveModelCancerRelated1993},
though there are always exceptions \citep{eysenbach09}

@@

Active, directed searching by individuals to obtain information is sparsely
discussed in the sociological literature. Pejtersen \citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar
of library and information science, theorized that there are 5 strategies for
searching for information. The most common strategy is browsing, where people
follow leads based on associations without premeditation. Another strategy is
analytical, which includes an explicit consideration of all facets of the
question to guide a search. The empirical method guides the search based on
tactics that were successful in past research. The known site strategy is to go
to the direct source of the information if known. And finally, the similarity
method is to find information based on another similar question that already has
an answer. These 5 strategies vary in their demands for prior knowledge,
cognitive processing, memory, and time spent. While this theory is aimed at
finding information in a library setting, scholars have extended the theory to
other fields and validated the framework
\citep{fidelHumanInformationInteraction2012}; the frame is a useful beginning point
for my theories of information search through network activation or through
computer-mediated communication.

@@

@@

There are important factors that can influence information-seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}
. UGT
posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s  \citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible with
Lazarsfeld and Katz’s theory of two-step flow \cite{katzPersonalInfluencePart1955}
because people can choose their media and the opinion leaders they follow.
Modern-day theorists have extended UGT theory and classified the uses and
gratifications of the internet and of social media. \citet{staffordDeterminingUsesGratifications2004} theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties. \citet{leungGenerationalDifferencesContent2013} theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

Adapting these facets of UGT and social support to my own case, I theorize that
online search allows for increased anonymity, a lowered social cost, and the
potential avoidance of embarrassment and other negative social interactions,
especially in the case on search engines. \citet{rainsCopingIllnessDigitally2018}
finds that patients tend to search for
technical information about an illness online but they then turn to their social
network for experiential information from others facing similar circumstances in
the case of cancer. The type of information sought is therefore important.
If specific expertise on a specific topic is desired by a searcher, they may
reach out to personal connections that they see as expert such as a doctor, or
if an individual distrusts the medical establishment, they may be more likely to
activate informational support among their social network or turn to online
groups that validate their worldview \citep{bogersHowSocialAre2014}. Finally, UGT and
Brasher's definition of social support \citeyearpar{brashersInformationSeekingAvoiding2002} help us to theorize that the
psychosocial needs like identity management or relational maintenance of an individual may influence their chosen information search vehicle: when the informational need is related to
forming and deepening social ties search is likely to be done from network ties.

@@

The data used for this research project are based on original survey data
sampled between December 03, 2021 through
December 12, 2021. This survey was hosted on Qualtrics and
participants were paid and recruited using Amazon Turk (MTurk). The total valid
survey responses (\emph{n} = 948) were selected from a total of 1,066
respondents; some responses were disqualified due to a few factors such as
detected usage of a VPN, random answer clicking (determined by illogical
responses), poor quality typed responses (e.g., social network alters
consistently named random nouns), or taking the survey more than once. The same
is slighted gender unbalanced, slightly skewing towards a male sample. For the
respondents who provided their zip code (p = 0.98), the sample is quite balanced with a slight skew towards MTurkers in the South (p = 0.41).

The survey took an average of 24.48 minutes with a standard deviation of 13.23 minutes. The shortest valid survey took 3.75 minutes and the longest took 111.08 minutes. Participants were paid \$6.00 for their time after Amazon administrative fees, funded by a Grant awarded to Kelsey E. Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social
Science and the Russell Sage Foundation. The main portion of this survey replicates the book, Someone to Talk To \citep{smallSomeoneTalk2017} by expanding on Small's finding that people draw on much broader sources than ``important people'' for support by segregating weak-tie social support into instrumental, emotional, and informational support \citep[see][]{houseStructuresProcessesSocial1988}. The latter
part of the survey focuses on resource activation for the specific case-study of
information during the Covid-19 pandemic analyzed in this paper.

\input{tables/paper2/table-1-desc}

@@

Further dependent variables segment the above question into multiple options;
``How did you look for information about the Covid-19 vaccine?'' Respondents were
posed with 5 responses and `other,' of which they could select multiple. The
largest proportion, 44\%, asked their `doctor or another health professional' (95\% Confidence Interval = \{41\%, 47\%\}). About 42\% said they asked, `a person
like friend, neighbor, or family member that {[}they{]} know' (95\% Confidence
Interval = \{39\%, 45\%\}). An additional 41\% searched `for {[}their{]} question
using an online search engine such as Google or Bing' (95\% Confidence Interval
= \{38\%, 45\%\}). About a quarter of the sample, 27\%, `posted queries in an
online discussion group, listserve, or other online forum like a Facebook Group
or Subreddit' (95\% Confidence Interval = \{24\%, 30\%\}). And finally, 18\% of the sample `posted queries on a social networking site such as Facebook timeline, Twitter status update, or LinkedIn' (95\% Confidence Interval = \{16\%, 21\%\}).
Much of the question wording and the specific categories of search were inspired
by ICPSR project 37220 \citep{scanlon19}.

\input{tables/paper2/table-2-desc}

@@

Another Dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received or plans to receive a vaccination against Covid-19. For this survey, the number of doses or timeline of receipt were less
relevant to the research question. This variable instead focuses on intent or
opinion about the vaccine. About 87\% have a
positive view about the vaccine. This construct is made through the combination
of two survey items. The first item is actual vaccination status, obtained through
the question `Did you receive a Covid-19 vaccine?'
84\% of the sample said that
they had indeed received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}). As the national vaccination rate is closer to 75\% \citep{cdc20}, this indicates some bias in our sample that must be
acknowledged: either MTurkers are more likely to be vaccinated that the normal
population (sampling bias) or there is some conformity bias in the responses
causing survey takers to provide false answers. The second survey item that
contributes to `Vaccination Outlook' was only given to those who had not
responded `yes' to the to their vaccination status. These respondents were asked `Do you
plan to receive a vaccine for the prevention of the Covid-19 virus?' Of those
who were asked this question (n = 147), 9\% said they were `definitely yes' getting the vaccine;
9\% said they were `probably yes' going to receive vaccine. The rest of the sample was more unsure: 15\% said they `Might or might not,' 26\% said `Probably not,' and finally 41\% said they would `definitely not' receive the vaccine. The variable `Vaccination Outlook' indicates that either the respondent received a Covid-19 vaccine or
either probably or definitely will in the future.

@@

My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-desc}
\& \ref{tab:table-2-desc}, I present descriptive statistics for all study
variables, including variable ranges, means, and standard deviations. For this
paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
fit a series of Binomial Generalized Linear Models \citep{venables2002a}. In Table \ref{tab:table-model-1}\footnote{All tables in this paper were created with the modelsummary package in \texttt{r} \citep{modelsummary}}
, I fit a logistic regression model predicting
whether someone sought information about Covid-19 using their sources of
information (`Received info') as well as various demographic variables such as
age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
the relationship between the coefficients and information seeking.\footnote{Figures in this paper were all created using the \texttt{r} packages jtools \citep{jtools} and ggplot2 \citep{wickham_etal, wickham11}}.
In Table \ref{tab:model-2-phi} I disaggregate information seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about Covid-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient \citep{warrens08}, otherwise
known as a mean square contingency coefficient which is used to investigate the
degree of association between two binary variables.\footnote{To calculate the Phi
  Coefficient, I utilize the Psych \texttt{r} package \citep{psych}} I then investigate the
associations between my predictors and the 5 information search vehicles by
modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook. Figure \ref{fig:plot-model-3} then
illustrates the relationship between the coefficients and vaccination outlook.

@@

\input{tables/paper2/table-model-1}

\begin{figure}
{\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-1-1}}
\caption{Plot of Coefficients, Model 1}\label{fig:plot-model-1}
\end{figure}

@@

\input{tables/paper2/model-2-phi}

To further investigate how people search for information, I asked those who had
sought information out intentionally, ``How did you look for information about
the Covid-19 vaccine?'' Because respondents could select as many responses as
applicable, each response is recorded as a dichotomous variable. Table
\ref{tab:table-1-desc} reveals differences in the prevalence of usage of the
various information seeking vehicles: Around 40\% of the sample has inquired for
information from a doctor, a person, or using online search tool (44\%, 42\%, 41\%) while my
respondents used vehicles like online forums (27\%) and social networking sites (18\%)
to seek out information at significantly lower rates. To investigate how each
Information Search Vehicle are related to each other using the Phi Coefficient
(\(\\phi\)) of binary association between each Information Search Vehicle pair.
The Phi coefficient can be interpreted like a correlation coefficient, with
numbers closer to -1 or positive one indicating a very strong relationship
(Warrens 2008). Table \ref{tab:model-2-phi} shows the results of these
coefficients. Out of the five information search vehicles investigated, there is
evidence that the vehicles are distinctly different concepts because most
coefficients fall under 0.3, the general rule of thumb for correlation
coefficients to indicate a relationship. There does seem to be a relationship
between Online Forums and Social Networking Sites, possibly due to an
individual's propensity to use online networks over in-person networks. These
coefficients indicate a weak relationship between any two vehicles of
information search and that respondents in my sample utilize each of these a
little bit differently.

\input{tables/paper2/table-model-2}

@@

\input{tables/paper2/table-model-3}
